The design and implementation of standards-based Grid single sign-on using federated identity

### 2009-05-01 doc/sec/papers/GRID09/paper.tex
little more text

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related web services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Although there are many SOAP
implementations such as AxisJava, gSOAP, XSOAP4, etc.., it is not the goal of this paper to do a
complete comparison between HED and all the other SOAP implementations, so we use Axis2/C (v1.5.0) to
demonstrate the performance of HED.

@@

The two ``echoString'' services run in a test machine equipped with a 3GHz Intel
Pentium dual-core CPU and 2GB memory, Red Hat Enterprise Linux 5. The client runs in another
machine equipped with 2.0GHz AMD Athlon CPU and 1GB memory, Red Hat Enterprise Linux 5. The
Axis2/C service is run using the httpd module on Apache Http Server version 2.2.11 instance. We use all the
default configurations in the Apache Http Server.

>>>>

\subsection{Performance comparison between HED and Axis2/C}
\label{sec:perhedandaxis}
Since the implementation of HED includes an alternative SOAP implementation
which is the base of the security related web services described in this paper, it is useful to
compare the performance of HED and other SOAP implementations. Here we compare 
the performance of HED and Axis2/C (v1.5.0), because we need to demostrate that the performance of HED
is at least comparable to other implementations. We do not compare the performance of HED 
with other SOAP implementations such as AxisJava, gSOAP, XSOAP4, etc., because a complete 
performance comparison between HED and all the other SOAP implementations is not the main 
goal of this paper to achieve, and a partial performance comparison is enough. Another reason
of choosing Axis2/C is because it is also implemented in C/C++ programming language.

@@

The two ``echoString'' services run in a test machine equipped with a 3GHz Intel
Pentium dual-core CPU and 2GB memory, Red Hat Enterprise Linux 5. The client runs in another
machine equipped with 2.0GHz AMD Athlon CPU and 1GB memory, Red Hat Enterprise Linux 5. The
Axis2/C service is run using the httpd module on Apache Http Server version 2.2.11 instance. 
We use all the default configurations in the Apache Http Server, and complie Axis2/C
with default options except specifying the ``--with-apache2'' option.
